Ontology Matching Paper

### 2016-05-08 milestone3/paper/paper.tex
data linking paper stuff

\subsection{Data Linkage}

>>>>

\subsection{Data Linkage}
In this section the developed Data Linkage system is presented.
It interlinks our dataset with two other datasets from groups 13 and 15. We
decided to implement the linking workflow and procedures using the
\textit{Silk framework}\footnote{\url{http://silkframework.org/}} which captions
itself as ``The Linked Data Integration Framework''. Silk is an open source
project for integrating heterogeneous data sources and among its use cases is
generating links between Linked Data sources, which is exactly within our needs.
Moreover Silk provides the user with a nice and friendly Web-based GUI and a visual
editor for linkage rules.

To link two Linked Datasets using Silk first we need to define their sources,
e.g. using a SPARQL endpoint or uploading an RDF dump. Then it is possible to
create linkage rules by applying four different kind of operations:
\begin{enumerate}
	\item path-like queries to retrieve values;
	\item transformations over those values (e.g. to-lowercase, tokenization);
	\item comparators over values (e.g. Levenshtein distance, Jaccard
		coefficient, equality);
	\item aggregators over comparators output (e.g. average, minimum, maximum).
\end{enumerate}
It is also possible to specify a threshold for the comparator's output score,
its weight when computing an aggregation for it or whether it is required that a
value exists for that block\footnote{We say block because Silk uses a visual
editor with block-shaped functionalities.}.

\subsubsection{Linking the Cultural Dataset}
This dataset has a domain in part similar to our so the linking procedure
is trivial and reduces to a check on the \texttt{rdfs:label} and some other
property. An example Silk linkage rule is shown in Figure \ref{fig:link_event_g10}
that matches events; in this case the match is checked against
\texttt{rdfs:label} and \texttt{dc:title}.
%TODO link other entities

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{img/link_event_g10.png}
	\caption{Silk linkage rules for events in group 10's dataset.}
	\label{fig:link_event_g10}
\end{figure}

\subsubsection{Linking the Tourist Safety Dataset}
In spite being about a different domain, this dataset can still be linked with
ours for what concerns events and locations / venues. Indeed the overlap between
events in this dataset and ours is big and we are able to match a big proportion
of entities by using a linkage rule similar to that shown in Figure
\ref{fig:link_event_g10} but using \texttt{rdfs:label} for both data sources.

\subsubsection{Linking the Activity Finding Dataset}
For events the linkage rule is less trivial and immediate than that for the
Cultural Dataset and involves the use of more properties and an aggregator as
shown in Figure \ref{fig:link_event_g15}.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{img/link_event_g15.png}
	\caption{Silk linkage rule for events in the Activity Finding Dataset.
		\texttt{sourcePath2} contains
		\texttt{/schema:location/schema:streetAddress} while
		\texttt{targetPath2} contains
		\texttt{/g6v:hasVenue/dbo:location/dbo:address}.}
	\label{fig:link_event_g15}
\end{figure}
